Verification of Stencil Computations through Spatial Specifications

### 2016-07-06 paper.tex
expand on ML

Our terminology of \emph{indexing schemes} and
\emph{unification} are by analogy
with the \emph{type schemes} and \emph{type unification} of
ML~\cite{milner1978theory}, though our notion is much more rigid.

>>>>

Our terminology of \emph{indexing schemes} and
\emph{unification} are by analogy
with the \emph{type schemes} and \emph{type unification} of
polymorphic types in ML~\cite{milner1978theory}. Our notion is
much more rigid however, there is only one way to unify two
index schemes in our model.
